Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
more drl

@@

With any fixed policy function, the agent will traverse a path 
$\tau=(s_0,\ a_0,\ s_1,\ a_1\ \dots,\ s_{t_{\text{fin.}}})$ 
sampled randomly from the distribution
\begin{align*}
  p_\pi(\tau) = 
  d(s_0) \prod_{t=0}^{ t_{\text{fin.}}-1 }
  \pi( a_t | s_t ) T( s_{t+1} | s_t, a_t ).
\end{align*}
Reinforcement learning seeks to optimize $\pi$ such that the expected rewards are maximal,
$$  
  \pi^* = \mathrm{argmax}\ \mathbb{E}_{\tau\sim p_\pi}[R(\tau)],
$$
where
$$
  R(\tau) = \sum_{t=0}^{ t_{\text{fin.}}-1 } \gamma^t r(a_t, s_t)
$$
is the cumulative reward of path $\tau$.
The function $J(\pi):=\mathbb{E}_{\tau\sim p_\pi}[R(\tau)]$ is called the *value function*.

@@

The policy function $\pi$ often lives in a high- or infinite-dimensional space.
This makes it unfeasible to directly optimize $\pi$.
In practice, an alternative approach is used: $\pi$ is optimized over a much lower-dimensional parametrized family of functions.
Deep reinforcement learning uses this strategy, focusing on function families parametrized by neural networks. (See Fig. \ref{tbd}.)

>>>>

RL figures:
- schematic of RL (a-la previous marcus paper Fig 1)
- Neural network optimization figure

@@

With any fixed policy function, the agent will traverse a path 
$\tau=(s_0,\ a_0,\ s_1,\ a_1\ \dots,\ s_{t_{\text{fin.}}})$ 
sampled randomly from the distribution
\begin{align*}
  p_\pi(\tau) = 
  d(s_0) \prod_{t=0}^{ t_{\text{fin.}}-1 }
  \pi( a_t | s_t ) T( s_{t+1} | s_t, a_t ).
\end{align*}
Reinforcement learning seeks to optimize $\pi$ such that the expected rewards are maximal,
$$  
  \pi^* = \mathrm{argmax}\ \mathbb{E}_{\tau\sim p_\pi}[R(\tau)],
$$
where,
$$
  R(\tau) = \sum_{t=0}^{ t_{\text{fin.}}-1 } \gamma^t r(a_t, s_t),
$$
is the cumulative reward of path $\tau$.
The function $J(\pi):=\mathbb{E}_{\tau\sim p_\pi}[R(\tau)]$ is called the *value function*.

@@

The policy function $\pi$ often lives in a high- or even infinite-dimensional space.
This makes it unfeasible to directly optimize $\pi$.
In practice, an alternative approach is used: $\pi$ is optimized over a much lower-dimensional parametrized family of functions.
Deep reinforcement learning uses this strategy, focusing on function families parametrized by neural networks. (See Fig. \ref{tbd}.)
<!-- The figure should kinda explain how the parametrization arises, and how gradient ascent is used. Maybe namedrop backpropagataion for the sake of usefulness to the reader? -->

Since our state and observation spaces are continuous, we will focus on deep reinforcement learning throughout this paper.
Specifically, we parametrize $\pi$ using a XXXX neural network and use the *proximal policy optimization (PPO)* algorithm to optimize $\pi$.
Within the RL literature there is a wealth of algorithms from which to choose from, each with its pros and cons.
Here we have focused on a single one of these for the sake of particularity---to draw a clear comparison between the RL-based and the classical fishery management approaches.
In practice, further improvements can be expected by a careful selection of the optimization algorithm.
